Individualized Measures of Partisan Fairness and Utility in Redistricting

### 2021-08-31 paper/paper.Rmd
explore NJ

---
title: Individualized Measures of Partisan Fairness and Utility in Redistricting (??)
authors:
  - name: Cory McCartan
    thanks: Footnote stuff
    department: Department of Statistics
    affiliation: Harvard University
    location: Cambridge, MA
    email: cmccartan@fas.harvard.edu
  - name: Christopher T. Kenny
    department: Department of Government
    affiliation: Harvard University
    location: Cambridge, MA
    email: christopherkenny@fas.harvard.edu
abstract: |
  Enter the text of your abstract here.
keywords:
  - partisan fairness
  - representation
  - redistricting simulation
  - individual standing
bibliography: references.bib
biblio-style: unsrt
output: 
  rticles::arxiv_article:
    keep_tex: true
    includes:
      in_header: "header.tex"
    latex_engine: pdflatex
---

>>>>

---
title: Individualized Measures of Partisan Fairness and Utility in Redistricting
authors:
  - name: Cory McCartan
    thanks: Footnote stuff
    department: Department of Statistics
    affiliation: Harvard University
    location: Cambridge, MA
    email: cmccartan@fas.harvard.edu
  - name: Christopher T. Kenny
    department: Department of Government
    affiliation: Harvard University
    location: Cambridge, MA
    email: christopherkenny@fas.harvard.edu
abstract: |
  Enter the text of your abstract here.
keywords:
  - partisan fairness
  - representation
  - redistricting simulation
  - individual standing
bibliography: references.bib
biblio-style: unsrt
output: 
  rticles::arxiv_article:
    keep_tex: true
    includes:
      in_header: "header.tex"
    latex_engine: pdflatex
---
